Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-27 edubots_surveys.Rnw
Hook for folloup
Adds intro

@@

\section{State of the art}

@@

\section{Methodology}

@@

\section{Results}

>>>>

The rest of the paper is organized as follows. Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom. The methodology used in the survey is presented in Section \ref{sec:meth}, and the results of the survey are presented next in Section \ref{sec:res}. Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.

@@

\section{State of the art}
\label{sec:soa}

@@

\section{Methodology}
\label{sec:meth}

@@

\section{Results}
\label{sec:res}
